\newcommand{\skillsection}[1]{\vspace{2mm}\textbf{\large #1}}
\cvsection{Technical Skills}
\begin{itemize}
  \item \skillsection{Languages:} Python (Numba/JIT), SQL, Java, JavaScript
  \item \skillsection{AI \& GenAI:} Hugging Face, Ollama, XGBoost, Scikit-learn, Optuna, Model Validation
  \item \skillsection{Statistics \& Research:} Bayesian Inference (ArviZ), MLE, Survival Analysis, Pytest, Hypothesis Testing
  \item \skillsection{Data Science:} Pandas, NumPy, Matplotlib, Seaborn, Plotly, Bokeh, Streamlit
  \item \skillsection{Web \& Tools:} Git, Docker, Sphinx, REST APIs, Postman, React.js, HTML/CSS
  \item \skillsection{Core Concepts:} Data Structures, Algorithms, Code Refactoring, Statistical Analysis
\end{itemize}

\cvsection{Achievements}
\smallskip
\begin{itemize} 

\item  \textbf {"First Runner-Up in  Hack With Uttarakhand (Team Code Heist)} - led a 36-hour offline hackathon with innovative problem solving and teamwork.'

\smallskip
\item Contributed to \href{https://www.notion.so/Open-Source-Contributions-Piyush-Panwar-1f6300c37fe680dd8c7ce6af712e95ae?pvs=4}{\textbf{[ Open Source ]}} initiatives including {\textbf{HacktoberFest, GirlScript}}, enhancing real-world software development skills. 

\end{itemize}

\cvsection{Projects}
\cvproject{\href{https://github.com/PiyushPanwarFST/ml-project-credit-risk-modeling}{Credit Risk Prediction System \faExternalLink}}
\begin{itemize}
  \item \textbf{Python | Scikit-learn | XGBoost | Optuna}
  \item Developed an end-to-end credit risk scoring engine that classifies borrowers into four risk tiers, predicting default probabilities and assigning credit scores (300–900).
  \item Engineered critical financial features (e.g., Loan-to-Income, Utilization Ratios) and leveraged \textbf{Optuna} for Bayesian hyperparameter optimization to maximize model AUC-ROC.
  \item Designed and deployed an dashboard using \textbf{Streamlit}, providing real-time risk analytics and AI insights for loan approval decisions.
\end{itemize}
\smallskip
\smallskip

\cvproject{\href{https://github.com/PiyushPanwarFST/ml-project-premium-prediction}{Health Insurance Premium Prediction \faExternalLink}}
\begin{itemize}
  \item \textbf{Python | XGBoost | Linear Reg. | Statistics}
  \item Built a high-precision prediction model achieving \textbf{98\% accuracy} & addressing high-error through strategic data ("Young" vs "Rest").
  \item Significantly reduced extreme prediction errors (from 27\% to 2\%) by conceptualizing and integrating a domain-informed \textbf{"Genetical Risk"} feature for the under-25 demographic.
  \item Utilized \textbf{Variance Inflation Factor (VIF)} analysis to eliminate multicollinearity and implemented a hybrid approach to ensure model stability and interpretability.
\end{itemize}

\vspace{10 pt} % Extra space for better visual separation

\clearpage

\nocite{*}

\end{document}